---
title: "Pilot feasibility report: Orbis-to-Revelio matching of international joint ventures"
subtitle: "Differentiated international integration in IJVs, Stage 4"
date: today
format:
  docx: default
  html: default
execute:
  echo: false
  warning: false
knitr:
  opts_knit:
    root.dir: "../.."
params:
  pilot: "main"
---

```{r setup}
#| include: false
source("code/R/00_setup.R")
TAG <- if (params$pilot == "main") "" else paste0(params$pilot, "-")
pin <- function(name) file.path(paths$interim, paste0("pilot-", TAG, name))
s  <- readRDS(pin("summary.rds"))
orbis <- fread(tail(sort(list.files(paths$raw, paste0("^orbis-pilot-", TAG, "[0-9].*[.]csv$"), full.names = TRUE)), 1),
               colClasses = list(character = c("jv_bvdid", "parent_bvdid", "guo_bvdid")))
frame <- fread(tail(sort(list.files(paths$interim, "^wrds-ijv-frame-2.*[.]csv$", full.names = TRUE)), 1),
               select = c("jv_bvdid", "excl_jv"), colClasses = "character")
groups <- fread(tail(sort(list.files(paths$interim, "^wrds-ijv-frame-groups-.*[.]csv$", full.names = TRUE)), 1),
                colClasses = list(character = "jv_bvdid"))
review <- fread(pin("jv-review-tier.csv"))
# Population the pilot represents: the whole eligible frame for the main
# pilot; for the large pilot, the screened pool (headcount >= 100, at least two
# parents in Revelio, not in the main pilot).
if (params$pilot == "large") {
  scr <- fread(tail(sort(list.files(paths$interim, "^wrds-large-screen-.*[.]csv$", full.names = TRUE)), 1),
               select = c("jv_bvdid", "parent_in_revelio"), colClasses = list(character = "jv_bvdid"))
  pool_ids <- scr[, .(k = sum(parent_in_revelio)), by = jv_bvdid][k >= 2, jv_bvdid]
  groups <- groups[jv_bvdid %in% pool_ids]
}
pop_n <- nrow(groups)
tier_labels <- c(auto = "Automatic name matches",
                 auto_plus_strong = "Plus strong website matches",
                 auto_plus_review = "Plus all review-tier matches")
jv_frame <- unique(frame, by = "jv_bvdid")
n_cand <- nrow(jv_frame)
excl <- jv_frame[, .N, by = .(reason = fifelse(is.na(excl_jv) | excl_jv == "", "eligible", excl_jv))][order(-N)]
pct <- function(x, d = 0) paste0(format(round(100 * x, d), nsmall = d), "%")

# Per-JV detail by tier, from the origin files written by 01_pilot_matching.R.
detail <- rbindlist(lapply(names(s$by_tier), function(t) {
  g <- fread(pin(sprintf("origin-%s.csv", t)), colClasses = list(character = "jv_bvdid"))
  g[, .(n_emp = uniqueN(user_id), n_years = uniqueN(year),
        emp_parent_a = uniqueN(user_id[origin == "parent_a"]),
        emp_parent_b = uniqueN(user_id[origin == "parent_b"])), by = jv_bvdid][, tier := t]
}))
detail <- merge(detail, unique(orbis[, .(jv_bvdid, exposure_group, jv_country)], by = "jv_bvdid"), by = "jv_bvdid")
# Intra-group arrangements: all parents share one Orbis global ultimate owner.
# They are subsidiaries split across group entities, not IJVs, and are
# excluded from the usable counts.
intra <- orbis[, .(intra_group = uniqueN(guo_bvdid) < 2), by = jv_bvdid]
detail <- merge(detail, intra, by = "jv_bvdid")
detail[, usable_any := n_emp >= const$min_ijv_emp & n_years >= const$min_years]
detail[, usable := usable_any & !intra_group]
usable <- detail[usable == TRUE]
tier_tab <- rbindlist(lapply(names(s$by_tier), function(t) {
  th <- s$by_tier[[t]]$thresholds; u <- usable[tier == t]
  data.table(Tier = tier_labels[[t]], `JVs matched` = th$jvs_matched, `JVs with workforce data` = th$jvs_with_data,
             `Usable, incl. intra-group` = detail[tier == t & usable_any == TRUE, .N],
             `Usable IJVs` = u[, .N],
             `Usable, staff from one parent or more` = u[emp_parent_a + emp_parent_b >= 1, .N],
             `Usable, staff from both parents` = u[emp_parent_a >= 1 & emp_parent_b >= 1, .N])
}))
# Projection to the frame: unweighted, and weighted by exposure group because
# the pilot oversamples exposed JVs.
grp_n <- groups[, .(N_frame = .N), by = exposure_group]
proj <- rbindlist(lapply(names(s$by_tier), function(t) {
  rates <- merge(orbis[, .(n_pilot = uniqueN(jv_bvdid)), by = exposure_group],
                 usable[tier == t, .(n_usable = .N, n_both = sum(emp_parent_a >= 1 & emp_parent_b >= 1)), by = exposure_group],
                 by = "exposure_group", all.x = TRUE)
  rates[is.na(n_usable), `:=`(n_usable = 0L, n_both = 0L)]
  rates <- merge(rates, grp_n, by = "exposure_group")
  data.table(Tier = tier_labels[[t]],
             `Usable, unweighted` = round(sum(rates$n_usable) / sum(rates$n_pilot) * pop_n),
             `Usable, weighted` = round(sum(rates$n_usable / rates$n_pilot * rates$N_frame)),
             `Both parents, weighted` = round(sum(rates$n_both / rates$n_pilot * rates$N_frame)))
}))
pg <- s$parents_in_group
```

## Purpose

The research design requires a pilot before the hypotheses are finalized,
because the main feasibility risk is entity matching and workforce coverage
rather than the statistical model. This report answers four questions. How
many pilot IJVs and parents can be identified as distinct Revelio entities?
How many observable employees and years does each matched IJV have? How many
IJV-function-year and IJV-seniority-year cells survive the minimum cell
sizes? Can parent-origin staffing be reconstructed for a usable share of
employees?

## Sample frame

Orbis Crossborder Investment is not part of the WRDS subscription, so the
frame comes from the current ownership links in the Orbis large and medium
company libraries (rules in `data/codebook.md`). The ownership screen
returned `r format(n_cand, big.mark = ",")` candidate companies. After
excluding JVs with a non-corporate parent, financial-sector JVs and
intra-group arrangements whose parents share one global ultimate owner,
`r format(s$frame_eligible, big.mark = ",")` remained eligible.
`r if (params$pilot == "large") paste0("This second pilot was drawn from the large-JV stratum: eligible JVs not in the first pilot with an Orbis headcount of at least 100 and at least two parents found in Revelio by name, directly or through their global ultimate owner. That stratum holds ", format(pop_n, big.mark = ","), " JVs.") else ""`
The pilot drew `r s$pilot_n` JVs, oversampling JVs exposed to the shortlisted
shocks. In `r intra[intra_group == TRUE, .N]` of them all parents share one
global ultimate owner. These are subsidiaries held through two group
entities rather than IJVs, and they are excluded from the usable counts.

```{r}
knitr::kable(excl, col.names = c("Frame status", "JVs"), caption = "Frame exclusions")
knitr::kable(orbis[, .(JVs = uniqueN(jv_bvdid)), by = .(`Exposure group` = exposure_group)][order(-JVs)],
             caption = "Pilot JVs by exposure group")
```

The frame contains only JVs that are active today and still have a
multi-parent structure, and it uses the incorporation date and the current
equity share in place of the formation date and formation share.

## Match rates

```{r}
knitr::kable(s$match_totals, caption = "Pilot entities with a Revelio candidate and an accepted match (guo = global ultimate owner of a parent)")
knitr::kable(s$match_rates, caption = "Accepted automatic matches by method")
knitr::kable(s$jv_rejected, caption = "JV candidates rejected by the guards")
```

The guards reject a JV candidate in another country and a candidate that is
the parent's own Revelio entity. Without them, several JVs matched their
parent and would have inherited the parent's workforce. A second, review tier
searches by the JV's website and by the first two name tokens in the host
country. It produced `r nrow(review)` candidates, of which
`r review[strong == TRUE, .N]` come from the website and have a close name.
They are listed in `data/interim/pilot-jv-review-tier.csv` for review.

## Workforce coverage and cell survival

A JV is usable if it has at least `r const$min_ijv_emp` observable employees
and at least `r const$min_years` observed years from its formation year
onward.

```{r}
knitr::kable(tier_tab, caption = "Coverage by matching tier")
cs <- rbindlist(lapply(names(s$by_tier), function(t) s$by_tier[[t]]$cell_survival[, tier := tier_labels[[t]]]))
knitr::kable(dcast(cs, tier + dimension ~ threshold, value.var = "cells_surviving"),
             caption = "Cells (JV x function or seniority x year) with at least 3, 5 and 10 employees")
```

## Parent-origin reconstruction

```{r}
os <- rbindlist(lapply(names(s$by_tier), function(t) s$by_tier[[t]]$origin_shares[, tier := tier_labels[[t]]]))
knitr::kable(dcast(os, origin ~ tier, value.var = "share")[, lapply(.SD, function(x) if (is.numeric(x)) round(x, 3) else x)],
             caption = "Share of JV person-years by origin of the employee")
knitr::kable(pg[, .N, by = .(Parents = parents, `Parents with a Revelio group` = parents_with_group)][order(Parents, `Parents with a Revelio group`)],
             caption = "Pilot JVs by number of parents found in Revelio")
knitr::kable(usable[tier == "auto_plus_strong", .(JV = jv_bvdid, Host = jv_country, Employees = n_emp, Years = n_years,
                                                 `From parent A` = emp_parent_a, `From parent B` = emp_parent_b,
                                                 Exposure = exposure_group)][order(-Employees)],
             caption = "Usable JVs, automatic plus strong matches")
```

```{r}
#| include: false
us <- usable[tier == "auto_plus_strong"]
osh <- s$by_tier$auto_plus_strong$origin_shares
sh <- function(o) { x <- osh[origin == o, share]; if (length(x)) x else 0 }
```

In the automatic plus strong tier, `r nrow(us)` JVs are usable.
`r us[emp_parent_a + emp_parent_b >= 1, .N]` of them have at least one
employee from a parent, and `r us[emp_parent_a >= 1 & emp_parent_b >= 1, .N]`
have employees from both parents. Parent-origin employees make up
`r pct(sh("parent_a") + sh("parent_b"), 1)` of person-years, external hires
`r pct(sh("external_host") + sh("external_intl"), 1)`, and employees with no
earlier position on record `r pct(sh("no_history"), 1)`. Localization can be
measured for every usable JV. Cross-parent integration and parent dominance
need employees from both parents.

## Projection to the frame

```{r}
knitr::kable(proj, caption = paste0("Projected usable JVs in the population the pilot represents (",
                                    format(pop_n, big.mark = ","), " JVs; weighted: by exposure group)"))
```

These projections rest on small pilot counts and inherit the survivor bias
of the frame. They are an order of magnitude, not an estimate.

## Go/no-go recommendation

The data-engineer agent's recommendation and its reasons are recorded in
`reviews/gate-4-pilot.md`. The PI decides.
