---
title: "Pilot feasibility report: Orbis-to-Revelio matching of international joint ventures"
subtitle: "Differentiated international integration in IJVs, Stage 4"
date: today
format:
  docx: default
  html: default
execute:
  echo: false
  warning: false
---

```{r setup}
source("code/R/00_setup.R")
s <- readRDS(file.path(paths$interim, "pilot-summary.rds"))
```

## Purpose

The research design (section 12 of the research idea) requires a pilot
before hypotheses are finalized, because the main feasibility risk is
entity matching and workforce coverage rather than the statistical model.
This report answers four questions. How many pilot IJVs and parents can
be identified as distinct Revelio entities? How many observable employees
and years does each matched IJV have? How many IJV-function-year cells
survive the minimum cell-size thresholds? Can parent-origin staffing be
reconstructed for a usable share of employees?

## Match rates

```{r}
knitr::kable(s$match_rates, caption = "Entities matched by method")
```

## Workforce coverage per matched IJV

```{r}
knitr::kable(s$thresholds, caption = "IJVs clearing the sample thresholds")
summary(s$cov_ijv[, .(n_emp, n_years, share_parent_origin, share_no_history)])
```

## Cell survival

```{r}
knitr::kable(s$cell_survival, caption = "IJV-function-year cells by minimum employees")
```

## Parent-origin reconstruction

The share of employees whose prior employer within the origin window can
be classified as parent A, parent B or external is reported in the
`share_parent_origin` and `share_no_history` columns above. The
data-engineer agent interprets these figures here, including the host
countries and functions where coverage is weakest.

## Go/no-go recommendation

The agent completes this section: projected usable IJVs if the full Orbis
population is five to ten times the pilot, whether the 200 to 800 target
is realistic, which thresholds the pre-analysis plan should adopt, and
whether an event-study design is feasible given the exposed dyads
observed in the pilot.
